A Longitudinal Analysis of the Privacy Paradox

### 2019-09-17 analyses/analyses.Rmd
- Substituted "RVAideMemoire" with "MVN" due to the former's incompatibility with newer R versions. - Added visual representation of the final model

```{r Packages, include = FALSE, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r multivardis}
mult_norm_test <- mshapiro.test(d_fs)
print(mult_norm_test)
```

@@

>>>>

```{r Packages, include = FALSE, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

```{r multivardis}
mult_norm_test <- mvn(d_fs)
print(mult_norm_test)
```

@@

```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
knitr::include_graphics("../figures/model_7.png")
```
